Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-02-03 awipev-CO2.Rmd

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
# xx <- read_tsv("../fb_server/ny-alesund/data/old/All_sensors_731101_2016-08-20.txt", skip=16, col_names=TRUE)
load(file = paste0(path, "fb_server/shinyroot/AWIPEV-CO2/nydata_hour_shiny.Rdata"))
#load(file = "../fb_server/shinyroot/AWIPEV-CO2/nydata_shiny.Rdata") #d
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT, NA), # beginning of data series for AT
         AT = ifelse(AT == "NaN", NA, AT), #3 columns are character
         pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT, ph_at_contros=pH_AT, pco2_contros=PCO2_corr_contros_filtered, zero_contros=PCO2_Corr_Zero2, 
         sal_fb=Salinity_filtered, temp_fb=Temperature_filtered, pH_durafet=HW_pH1_filtered, temp_insitu=Temp_SBE38_filtered)
```

@@

## SNAPO-CO2
We found that some analysed discrete seawater replicates for AT/CT, performed by SNAPO in Paris sometimes show a large difference between duplicates. Arbitrarily, we decided to take in consideration replicates with a standard deviation smaller than 10 µmoles.kg-1. In the other case (greater than 10 µmoles.kg-1), the closest replicate from the general trend will be kept with qflag_at/qflag_ct of 2 (correct analysis) and the farthest one will be rejected with a flag of 1. There are exceptions when it is difficult to decide which of the replicates need to be eliminated.

@@

##Script + data
<div style="text-align: justify">  
Here is reported all important modifications made on *ny-alesund_cc.*. This script is accessible via http://efoce-shiny.obs-vlfr.fr:8787/auth-sign-in.

>>>>

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
# xx <- read_tsv("../fb_server/ny-alesund/data/old/All_sensors_731101_2016-08-20.txt", skip=16, col_names=TRUE)
load(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/processed/nydata_hour.Rdata"))
#load(file = paste0(path, "fb_server/shinyroot/AWIPEV-CO2/nydata_hour_shiny.Rdata"))
#load(file = "../fb_server/shinyroot/AWIPEV-CO2/nydata_shiny.Rdata") #d
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT, NA), # beginning of data series for AT
         AT = ifelse(AT == "NaN", NA, AT), #3 columns are character
         pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT, ph_at_contros=pH_AT, pco2_contros=PCO2_corr_contros_filtered, zero_contros=PCO2_Corr_Zero2, 
         sal_fb=Salinity_filtered, temp_fb=Temperature_filtered, pH_durafet=HW_pH1_filtered, temp_insitu=Temp_SBE38_filtered)
```

@@

## SNAPO-CO2
Since November 2018, informations on weekly Ferrybox and monthly durafet/seaFET samplings are collected in a online document that can be consulted at anytime:

[weekly and monthly samplings](https://docs.google.com/spreadsheets/d/1bNh9q4bkNoh2ra78XC451EmGb9Q8kMf4ByBnKngeHOg/edit?usp=sharing)

We found that some analysed discrete seawater replicates for AT/CT, performed by SNAPO in Paris sometimes show a large difference between duplicates. Arbitrarily, we decided to take in consideration replicates with a standard deviation smaller than 10 µmoles.kg-1. In the other case (greater than 10 µmoles.kg-1), the closest replicate from the general trend will be kept with qflag_at/qflag_ct of 2 (correct analysis) and the farthest one will be rejected with a flag of 1. There are exceptions when it is difficult to decide which of the replicates need to be eliminated.

@@

##Script + data
<div style="text-align: justify">  
Here is reported all important modifications made on *ny-alesund_cc.*.
All documents concerning maintenance, tasks to do, calibration... are accessible by the AWIPEV staff on this link with special access:

[wiki document](https://spaces.awi.de/confluence/login.action?os_destination=%2Fpages%2Fviewpage.action%3FspaceKey%3DMOS%26title%3DWater%2Bsampling&permissionViolation=true)
